---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# elodea

<!-- badges: start -->
[![R-CMD-check](https://github.com/onestop-project/elodea/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/onestop-project/elodea/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/onestop-project/elodea/graph/badge.svg)](https://app.codecov.io/gh/onestop-project/elodea)
[![test-coverage](https://github.com/onestop-project/elodea/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/onestop-project/elodea/actions/workflows/test-coverage.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Project Status: Active](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)

<!-- badges: end -->

The goal of elodea is to clean and standardise published GBIF checklists. With elodea you can prepare checklists on alien species to create a unified checklist.

To get started, see:

- [Function
  reference](https://onestop-project.github.io/elodea/reference/index.html):
  overview of all functions.

## Installation

You can install the development version of elodea from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("onestop-project/elodea")
```

## Usage

With elodea you can **get** the taxonomic and distribution information of a published GBIF checklist.

Here we get the source taxa and distributions of the [Global Register of Introduced and Invasive Species - Cyprus](https://www.gbif.org/dataset/2f7ea7d1-a73f-46f6-b790-7339126a999f).

``` {r}
library(elodea)

datasetKey <- "2f7ea7d1-a73f-46f6-b790-7339126a999f"

taxa <- get_taxa(datasetKey)
distributions <- get_distributions(datasetKey, taxa)
```

Then you can **filter**/standardise both taxa and distributions with `filter_data()`, which will return a list with three data frames: `taxa`, `distributions` and `notes`. The first two data frames are the filtered taxa and distributions, while the `notes` data frame contains information on the filtering process. Check [`filter_data()`](https://onestop-project.github.io/elodea/reference/filter_data.html) for the filter details.

``` {r}
filter_data(taxa, distributions)
```

The notes can help improve the source checklist. The standardised taxa and distribution data can be used to build unified checklists by combining multiple checklists into a single checklist.

## Meta

- We welcome
  [contributions](https://onestop-project.github.io/elodea/CONTRIBUTING.html)
  including bug reports.
- License: MIT
- Get [citation
  information](https://onestop-project.github.io/elodea/authors.html#citation)
  for elodea in R doing `citation("elodea")`.
- Please note that this project is released with a [Contributor Code of
  Conduct](https://onestop-project.github.io/elodea/CODE_OF_CONDUCT.html). By
  participating in this project you agree to abide by its terms.
